Design, Implementation, and Evaluation of Open Power Quality

### 2020-08-03 manuscript.v5/energies-864131.tex
finished v5

@@

\bibitem[Delgado \em{et~al.}(2011)Delgado, Santos, de~Almeida, and
Figueira]{delgado_solutions_2011}
Delgado, J.; Santos, B.; de~Almeida, A.T.; Figueira, A.
\newblock Solutions to mitigate power quality disturbances resulting from
integrating intermittent renewable energy in the grid of {Porto} {Santo}.
\newblock In {Proceedings of the } 11th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilisation}, \hl{October 17, 2011}; pp. 1--6,
\newblock ISSN 2150-6655,
doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/EPQU.2011.6128870}{\detokenize{10.1109/EPQU.2011.6128870}}}.

\bibitem[Zavoda(2018)]{zavoda_power_2018}
Zavoda, F.
\newblock { Power {Quality} and {EMC} {Issues} with {Future} {Electricity}
{Networks}}. In {Proceedings of the } CIGRE, \hl{May 15, 2018}.

\bibitem[Nakafuji \em{et~al.}(2011)Nakafuji, Aukai, Dangelmaier, Reynolds,
Yoshimura, and {Ying Hu}]{nakafuji_back--basics_2011}
Nakafuji, D.; Aukai, T.; Dangelmaier, L.; Reynolds, C.; Yoshimura, J.; {
Hu, Y}.
\newblock “{Back}-to-basics”: {Operationalizing} data mining and visualization
techniques for utilities.
\newblock In {Proceedings of the }The 2011 International Joint Conference on Neural Networks, \hl{July 31, 2011}; pp. 3093--3098, doi:10.1109/IJCNN.2011.6033630.

@@

\bibitem[Elphick \em{et~al.}(2015)Elphick, Ciufo, Smith, and
Parera]{elphick_summary_2015}
Elphick, S.; Ciufo, P.; Smith, V.; Parera, S.
\newblock Summary of the economic impacts of power quality on consumers.
\newblock  In {Proceedings of the }2015 {Australasian} {Universities} {Power} {Engineering}
{Conference}, \hl{September 27, 2015}.

\bibitem[Laskar(2012)]{laskar_power_2012}
Laskar, S.H.
\newblock Power quality issues and need of intelligent {PQ} monitoring in the
smart grid environment.
\newblock In~{Proceedings of the }2012 47th
{International} Universities {Power} {Engineering} {Conference} ({UPEC}), \hl{September 4, 2012}; pp.~1--6.

@@

\bibitem[Thallam and Heydt(2000)]{thallam_power_2000}
Thallam, R.; Heydt, G.
\newblock Power acceptability and voltage sag indices in the three phase sense.
\newblock In {Proceedings of the } 2000 {Power} {Engineering} {Society} {Summer} {Meeting},
 \hl{July 16, 2000}; Volume~2, pp. 905--910, doi:10.1109/PESS.2000.867482.

@@

\bibitem[Dickens \em{et~al.}(2019)Dickens, Christe, and
Johnson]{dickens_transient_2019}
Dickens, C.; Christe, A.; Johnson, P.
\newblock A {Transient} {Classification} {System} {Implementation} on an {Open}
{Source} {Distributed} {Power} {Quality} {Network}.
\newblock  In Proceedings of the {Ninth} {International} {Conference} on {Smart}
{Grids}, {Green} {Communications} and {IT} {Energy}-aware {Technologies},
\hl{June 2, 2019}.

@@

\bibitem[Di~Manno \em{et~al.}(2015)Di~Manno, Varalone, Verde, De~Santis,
Di~Perna, and Salemme]{di_manno_user_2015}
Di~Manno, M.; Varalone, P.; Verde, P.; De~Santis, M.; Di~Perna, C.; Salemme, M.
\newblock User friendly smart distributed measurement system for monitoring and
assessing the electrical power quality.
\newblock In Proceedings of the 2015 {AEIT} {International} {Annual}
{Conference}, \hl{October 14, 2015}.

@@

\bibitem[Bilik \em{et~al.}(2007)Bilik, Koval, and Hula]{bilik_modular_2007}
Bilik, P.; Koval, L.; Hula, J.
\newblock Modular system for distributed power quality monitoring.
\newblock In {Proceedings of the } 9th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilization}, \hl{2007}.

\bibitem[Xu \em{et~al.}(2012)Xu, Xu, Xi, and Zhang]{xu_distributed_2012}
Xu, W.; Xu, G.; Xi, Z.; Zhang, C.
\newblock Distributed power quality monitoring system based on {EtherCAT}.
\newblock In {Proceedings of the }2012 {China} {International} {Conference} on {Electricity}
{Distribution}, \hl{2012}.

\bibitem[Suslov \em{et~al.}(2014)Suslov, Solonina, and
Smirnov]{suslov_distributed_2014}
Suslov, K.; Solonina, N.; Smirnov, A.
\newblock Distributed power quality monitoring.
\newblock In {Proceedings of the } {IEEE} 16th {International} {Conference} on {Harmonics} and
{Quality} of {Power}, \hl{2014}.

\bibitem[Sayied \em{et~al.}(2013)Sayied, Spaulding, and
Akbary]{sayied_power_2013}
Sayied, O.; Spaulding, J.; Akbary, B.
\newblock \hl{Power quality metrics calculations for the smart grid}. %%% Please add more detailed information.

@@

\bibitem[Bayindir \em{et~al.}(2016)Bayindir, Demirbas, Irmak, Cetinkaya, Ova,
and Yesil]{bayindir_effects_2016}
Bayindir, R.; Demirbas, S.; Irmak, E.; Cetinkaya, U.; Ova, A.; Yesil, M.
\newblock Effects of renewable energy sources on the power system.
\newblock In {Proceedings of the } 2016 {IEEE} {International} {Power} {Electronics} and {Motion}
{Control} {Conference} ({PEMC}), \hl{2016}; pp. 388--393, doi:10.1109/EPEPEMC.2016.7752029.

\bibitem[Farhoodnea \em{et~al.}(2012)Farhoodnea, Mohamed, Shareef, and
Zayandehroodi]{farhoodnea_power_2012}
Farhoodnea, M.; Mohamed, A.; Shareef, H.; Zayandehroodi, H.
\newblock Power quality impact of grid-connected photovoltaic generation system
in distribution networks.
\newblock In {Proceedings of the } 2012 {IEEE} {Student} {Conference} on {Research} and {Development}
({SCOReD}), \hl{2012}; pp. 1--6, doi:10.1109/SCOReD.2012.6518600.

>>>>

%%% I HAVE ADDED LOCATIONS AND DATES TO FOLLOWING CITATIONS

@@

\bibitem[Delgado \em{et~al.}(2011)Delgado, Santos, de~Almeida, and
Figueira]{delgado_solutions_2011}
Delgado, J.; Santos, B.; de~Almeida, A.T.; Figueira, A.
\newblock Solutions to mitigate power quality disturbances resulting from
integrating intermittent renewable energy in the grid of {Porto} {Santo}.
\newblock In {Proceedings of the } 11th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilisation}, Lisbon, Portugal, \hl{October 17, 2011}; pp. 1--6,
\newblock ISSN 2150-6655,
doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/EPQU.2011.6128870}{\detokenize{10.1109/EPQU.2011.6128870}}}.

\bibitem[Zavoda(2018)]{zavoda_power_2018}
Zavoda, F.
\newblock { Power {Quality} and {EMC} {Issues} with {Future} {Electricity}
{Networks}}. In {Proceedings of the } CIGRE, Paris, France, \hl{May 15, 2018}.

\bibitem[Nakafuji \em{et~al.}(2011)Nakafuji, Aukai, Dangelmaier, Reynolds,
Yoshimura, and {Ying Hu}]{nakafuji_back--basics_2011}
Nakafuji, D.; Aukai, T.; Dangelmaier, L.; Reynolds, C.; Yoshimura, J.; {
Hu, Y}.
\newblock “{Back}-to-basics”: {Operationalizing} data mining and visualization
techniques for utilities.
\newblock In {Proceedings of the }The 2011 International Joint Conference on Neural Networks, San Jose, California, \hl{July 31, 2011}; pp. 3093--3098, doi:10.1109/IJCNN.2011.6033630.

@@

\bibitem[Elphick \em{et~al.}(2015)Elphick, Ciufo, Smith, and
Parera]{elphick_summary_2015}
Elphick, S.; Ciufo, P.; Smith, V.; Parera, S.
\newblock Summary of the economic impacts of power quality on consumers.
\newblock  In {Proceedings of the }2015 {Australasian} {Universities} {Power} {Engineering}
{Conference}, Wollongong, Australia, \hl{September 27, 2015}.

\bibitem[Laskar(2012)]{laskar_power_2012}
Laskar, S.H.
\newblock Power quality issues and need of intelligent {PQ} monitoring in the
smart grid environment.
\newblock In~{Proceedings of the }2012 47th
{International} Universities {Power} {Engineering} {Conference} ({UPEC}), London, England, \hl{September 4, 2012}; pp.~1--6.

@@

\bibitem[Thallam and Heydt(2000)]{thallam_power_2000}
Thallam, R.; Heydt, G.
\newblock Power acceptability and voltage sag indices in the three phase sense.
\newblock In {Proceedings of the } 2000 {Power} {Engineering} {Society} {Summer} {Meeting}, Seattle, Washington,
 \hl{July 16, 2000}; Volume~2, pp. 905--910, doi:10.1109/PESS.2000.867482.

@@

\bibitem[Dickens \em{et~al.}(2019)Dickens, Christe, and
Johnson]{dickens_transient_2019}
Dickens, C.; Christe, A.; Johnson, P.
\newblock A {Transient} {Classification} {System} {Implementation} on an {Open}
{Source} {Distributed} {Power} {Quality} {Network}.
\newblock  In Proceedings of the {Ninth} {International} {Conference} on {Smart}
{Grids}, {Green} {Communications} and {IT} {Energy}-aware {Technologies}, Athens, Greece,
\hl{June 2, 2019}.

@@

\bibitem[Di~Manno \em{et~al.}(2015)Di~Manno, Varalone, Verde, De~Santis,
Di~Perna, and Salemme]{di_manno_user_2015}
Di~Manno, M.; Varalone, P.; Verde, P.; De~Santis, M.; Di~Perna, C.; Salemme, M.
\newblock User friendly smart distributed measurement system for monitoring and
assessing the electrical power quality.
\newblock In Proceedings of the 2015 {AEIT} {International} {Annual}
{Conference}, Naples, Italy \hl{October 14, 2015}.

@@

\bibitem[Bilik \em{et~al.}(2007)Bilik, Koval, and Hula]{bilik_modular_2007}
Bilik, P.; Koval, L.; Hula, J.
\newblock Modular system for distributed power quality monitoring.
\newblock In {Proceedings of the } 9th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilization}, Barcelona, Spain, \hl{October 9, 2007}.

\bibitem[Xu \em{et~al.}(2012)Xu, Xu, Xi, and Zhang]{xu_distributed_2012}
Xu, W.; Xu, G.; Xi, Z.; Zhang, C.
\newblock Distributed power quality monitoring system based on {EtherCAT}.
\newblock In {Proceedings of the }2012 {China} {International} {Conference} on {Electricity}
{Distribution}, Shanghai, China, \hl{September 10, 2012}.

\bibitem[Suslov \em{et~al.}(2014)Suslov, Solonina, and
Smirnov]{suslov_distributed_2014}
Suslov, K.; Solonina, N.; Smirnov, A.
\newblock Distributed power quality monitoring.
\newblock In {Proceedings of the } {IEEE} 16th {International} {Conference} on {Harmonics} and
{Quality} of {Power}, Orlando, Florida, \hl{October 1, 2014}.

\bibitem[Sayied \em{et~al.}(2013)Sayied, Spaulding, and
Akbary]{sayied_power_2013}
Sayied, O.; Spaulding, J.; Akbary, B.
\newblock \hl{Power quality metrics calculations for the smart grid}, Technical Report, ECE 401, Department of Electrical and Computer Engineering, Colorado State University, December 12, 2012. %%% Please add more detailed information.

@@

\bibitem[Bayindir \em{et~al.}(2016)Bayindir, Demirbas, Irmak, Cetinkaya, Ova,
and Yesil]{bayindir_effects_2016}
Bayindir, R.; Demirbas, S.; Irmak, E.; Cetinkaya, U.; Ova, A.; Yesil, M.
\newblock Effects of renewable energy sources on the power system.
\newblock In {Proceedings of the } 2016 {IEEE} {International} {Power} {Electronics} and {Motion}
{Control} {Conference} ({PEMC}), Varna, Bulgaria, \hl{September 25, 2016}; pp. 388--393, doi:10.1109/EPEPEMC.2016.7752029.

\bibitem[Farhoodnea \em{et~al.}(2012)Farhoodnea, Mohamed, Shareef, and
Zayandehroodi]{farhoodnea_power_2012}
Farhoodnea, M.; Mohamed, A.; Shareef, H.; Zayandehroodi, H.
\newblock Power quality impact of grid-connected photovoltaic generation system
in distribution networks.
\newblock In {Proceedings of the } 2012 {IEEE} {Student} {Conference} on {Research} and {Development}
({SCOReD}), Kuala Lumpur, \hl{December 13, 2012}; pp. 1--6, doi:10.1109/SCOReD.2012.6518600.
